\titleNameLong{}

### 2015-12-08 FinalProject/Tex/paper/paper.tex
Added conclusion

\section{Conclusions} \label{sec:conclusions}
\begin{itemize}
\item Mention what the survey talked about
  \begin{itemize}
  \item Background
  \item Overview
  \item Challenges
  \item Designs
  \end{itemize}
\item Explain changes occurring in field
\item Talk about what the future could hold
\end{itemize}

>>>>

\section{Conclusions} \label{sec:conclusions}
This survey article gave a brief overview of GPU architecture, general-purpose
computing on GPUs and the corresponding challenges, and current areas of
research in GPGPU.

GPGPU is a relatively young field but grows more popular each year. The main
struggles with GPGPU are maintaining high utilization of resources in the face
of complicated applications that are not easily mapped to GPU architectures
while keeping contention of other resources, especially those related to memory.
High memory pressure prevents GPUs from hiding memory latency and seriously
degrades performance.

Techniques within GPGPU continue to be developed focusing on a number of
different areas. While this survey has only scratched the surface, it has
provided a glimpse into current efforts to dynamically create helper warps and
thread-blocks, dynamically schedule warps and adjust the state of the SMs on the
fly, and use better compiler techniques to avoid divergence and produce better
mappings to GPU architectures. A couple other novel research areas such as data
compression and reducing memory contention were also discussed.

GPUs may have started out as specialized hardware for rendering graphics, but
they have begun to be used on much more diverse problems. If the challenges of
GPGPU can be overcome, significant performance improvements across a wide range
of applications could be unlocked.
